
\section{Design}

\subsection{API}

This application will include a HTTP endpoint that will allow users to access it remotely over the internet.

\subsection{Events}

This section will detail the various events offered by this application that can be used to wake specific devices.

\subsubsection{Schedules}

Users will want to schedule devices to turn on at recurring periods. This application will offer users the ability to set recurring days of the week and times at which a device should be woken.

\subsubsection{Scanning the LAN}

The vast majority of users will have a personal device, such as mobile phone, that will connect to their home router when they're nearby. This means that by listening for when devices join the local network, this application can determine when a user arrives home and can wake the relevant set of devices.
\x
Checking whether a device is in the network can be achieved using an ARP request and assuming that if the device doesn't respond then it can't be in the network.
\x
The user will configure devices to wake when they're personal device joins the network. Some examples would be their PC or various IoT devices around the home.

\subsubsection{Bluetooth}

Bluetooth is a short-range, low-bandwidth, low-power wireless communication protocol that is commonly found in battery powered devices. By allowing this application to search for bluetooth devices, it massvely increases the number of devices we can search for and removes the requirement from the previous section of being in the same LAN.
\x
To initiate a connection, a device will send an \textit{inquiry} message to the target and if the target is in discoverable mode then it will respond. A non-discoverable device will never respond to these messages;
however, the paper \textit{Detecting Non-Discorable Bluetooth Devices}~\cite{} showed that non-discoverable devices can be detected using an `enhanced brute force search attack' as long as you know the device's address. But, this solution is time consuming and wouldn't be a useful addition to this proejct.

\subsubsection{Environment Sensors}

It may be useful for devices to be triggered by environmental factors, such as detecting motion, room temperature, and light.
